Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-10 paper_io_sim.tex
updated title
Added simulation time results

%\title{Simulating the Linux page cache in distributed applications with WRENCH}
\title{Simulating the Linux page cache in distributed applications with WRENCH}

@@

        \subsection{Real application}
        \subsection{Overhead comparison}
        \tristan{Dzung, add your overhead measures here.}

>>>>

\title{Modeling the Linux page cache for accurate simulation of data-intensive applications}

@@

        \subsection{Real application}

        \subsection{Overhead comparison}
        As is the case for WRENCH, simulation time with WRENCH-cache scales
        linearly with the number of concurrent applications
        (Figure~\ref{fig:multi_time}, p \textless $10^{-24}$). However, the page
        cache model substantially increases the simulation time by
        application as can be seen by comparing regression slopes in
        Figure~\ref{fig:multi_time}. Interestingly, WRENCH-cache is faster with 
        NFS I/Os than with local I/Os, most likely due to the use of writethrough
        cache in NFS, which by-passes flushing operations.
        \begin{figure}
            \begin{subfigure}{\columnwidth}
                \centering
                \includegraphics[width=\linewidth]{result/multi/figures/simulation_time.pdf}
            \end{subfigure}
            \caption{Simulation time comparison. WRENCH-cache scales
            linearly with the number of concurrent applications, albeit
            with a higher overhead than WRENCH.}
            \label{fig:multi_time}
            \end{figure}
